\documentclass{article}
\usepackage{amsmath}
\usepackage[margin=1.0in]{geometry}
\usepackage{xcolor}

\begin{document}

\noindent
Does $\displaystyle \sum_{n=1}^\infty \frac{1}{n(n+2)}$
diverge, converge absolutely, or converge conditionally?

\subsection*{Solution 1}

Rewrite $\frac1{n(n+2)}$ using partial fraction decomposition:
\[ \frac1{n(n+2)} = \frac{A}{n} + \frac{B}{n+2}\]
So
\[ 1 = A(n+2) + Bn\]
Using $n=0$, we get $A =\frac12$. Using $n=-2$, we get $B=-\frac12$. So
\[ \frac1{n(n+2)} = \frac{\frac12}{n} - \frac{\frac12}{n+2}\]
Therefore, our original series can be rewritten:
$\displaystyle \sum_{n=1}^\infty \frac{1}{n(n+2)} =  \displaystyle \sum_{n=1}^\infty \left( \frac{1/2}{n} - \frac{1/2}{n+2} \right)$

\vskip20pt
\noindent
We appear to have a telescoping series. After cancellations, the $n$th term of the sequence of partial sums is:
\[ s_n = \frac{1/2}{1} + \frac{1/2}{2} - \frac{1/2}{n+1} - \frac{1/2}{n+2}\]
Thus,
\begin{align*}
\lim_{n \to \infty} s_n
&=  \lim_{n \to \infty} \left( \frac{1/2}{1} + \frac{1/2}{2} - \frac{1/2}{n+1} - \frac{1/2}{n+2}\right) \\
&=  \frac12 + \frac14 - 0 - 0\\
&= \frac34
\end{align*}
So, (by definition), the series $\displaystyle \sum_{n=1}^\infty \frac{1}{n(n+2)}$ converges, and we furthermore know that the sum is $\frac34$. Recall that it is unusual that we get to know the value of a convergent series.

Since $\sum |a_n| = \sum a_n$, the series $\displaystyle \sum_{n=1}^\infty \frac{1}{n(n+2)}$ converges absolutely.

\subsection*{Solution 2}

Note that $n(n+2) \geq n^2$ for all $n \geq 1$. So
\[ \frac1{n(n+2)} \leq \frac{1}{n^2}\]
The series $\displaystyle \sum_{n=1}^\infty  \frac{1}{n^2}$ converges by the $p$-test. Therefore, the series  $\displaystyle \sum_{n=1}^\infty \frac{1}{n(n+2)}$ converges by the Direct Comparison Test.

Since $\sum |a_n| = \sum a_n$, the series $\displaystyle \sum_{n=1}^\infty \frac{1}{n(n+2)}$ converges absolutely.

\end{document}%%%%%%%%%%%%%%%%%

\begin{align*}
L&=\lim_{n \to \infty} \sqrt[n]{|a_n|}\\
&= \lim_{n \to \infty} \sqrt[n]{\left| \right|}\\
\end{align*}


Since $\sum |a_n| = \sum a_n$, the series $\displaystyle \sum_{n=1}^\infty AAAAAAAAAAAAAA$ converges absolutely.

Since $|r| < 1$, the series ...  converges by the Geometric Series Test.

Since $|r| \geq 1$, the series ...  diverges by the Geometric Series Test.

The function $f(x)=\frac{}{}$ is continuous, positive, and decreasing on $[1,\infty)$.

\subsection*{Solution}

