\documentclass{article}
\usepackage{amsmath}
\usepackage[margin=1.0in]{geometry}
\usepackage{xcolor}

\begin{document}

\noindent
Does $\displaystyle \sum_{n=2}^\infty \frac{n^2+2}{n^3-1}$
diverge, converge absolutely, or converge conditionally?

\subsection*{Solution 1}

Consider the following string of equalities/inequalities:
\[ \frac1n = \frac{n^2}{n^3} \leq \frac{n^2}{n^3-1} \leq \frac{n^2+2}{n^3-1}\]
Why is each expression larger than the next? Either the numerator stayed the same with the denominator decreasing (by $1$) or the denominator stayed the same with the numerator increasing (by $2$). In summary,
\[ \frac1n \leq \frac{n^2+2}{n^3-1}.\]
Since the series $\sum \frac1n$ diverges by the $p$-series test, the series $\displaystyle \sum_{n=2}^\infty \frac{n^2+2}{n^3-1}$ diverges by the Direct Comparison Test.


\subsection*{Solution 2}

The series $\sum \frac1{n}$ diverges by the $p$-test. Let $a_n = \frac{n^2+2}{n^3-1}$ and $b_n = \frac1{n}$.
\begin{align*}
\lim_{n \to \infty} \frac{a_n}{b_n}
&= \lim_{n \to \infty} \frac{n^3+2n}{n^3-1}\\
&= \lim_{n \to \infty} \frac{3n^2+2}{3n^2} \text{ by l'hopital}\\
&= \lim_{n \to \infty} \frac{6n}{6n} \text{ by l'hopital}\\
&= \lim_{n \to \infty} \frac66 \text{ by l'hopital}\\
&= 1
\end{align*}
The Limit Comparison Test applies, since this limit was a positive, finite number. Therefore, the series $\sum \frac{n^2+2}{n^3-1}$ diverges by the Limit Comparison Test.




\end{document}%%%%%%%%%%%%%%%%%

\begin{align*}
L&=\lim_{n \to \infty} \sqrt[n]{|a_n|}\\
&= \lim_{n \to \infty} \sqrt[n]{\left| \right|}\\
\end{align*}

\begin{align*}
L&=\lim_{n \to \infty} \left|\frac{a_{n+1}}{a_n}\right|\\
&= \lim_{n \to \infty} \left| \right|\\
\end{align*}

\begin{align*}
\lim_{n \to \infty} a_n
&= \lim_{n \to \infty} \\
\end{align*}


Since $\sum |a_n| = \sum a_n$, the series $\displaystyle \sum_{n=1}^\infty AAAAAAAAAAAAAA$ converges absolutely.

Since $|r| < 1$, the series ...  converges by the Geometric Series Test.

Since $|r| \geq 1$, the series ...  diverges by the Geometric Series Test.

The function $f(x)=\frac{}{}$ is continuous, positive, and decreasing on $[1,\infty)$.

\subsection*{Solution}

