\documentclass{article}
\usepackage{amsmath}
\usepackage[margin=1.0in]{geometry}
\usepackage{xcolor}

\begin{document}

\noindent
Does $\displaystyle \sum_{n=2}^\infty \frac{2n}{n^2+1}$
diverge, converge absolutely, or converge conditionally?

\subsection*{Solution 1}

The function $f(x)=\frac{2x}{x^2+1}$ is continuous, positive, and decreasing on $[2,\infty)$.
\begin{align*}
\int_2^\infty \frac{2x}{x^2+1}\,dx
&= \lim_{t \to \infty} \int_2^t \frac{2x}{x^2+1}\,dx\\
&= \lim_{t \to \infty} (\ln|t^2+1| - \ln |2^2+1|)\\
&= \infty
\end{align*}
Since the integral $\displaystyle \int_2^\infty \frac{2x}{x^2+1}\,dx$ diverges, the series $\displaystyle \sum_{n=2}^\infty \frac{2n}{n^2+1}$ diverges by the Integral Test.

\subsection*{Solution 2}

Since $n^2 \geq 1$, by adding $n^2$ to both sides of this inequality
\[ 2n^2 \geq n^2 + 1\]
Dividing both sides of this ineqaulity by $n(n^2+1)$, we get
\[ \frac{2n}{n^2+1} \geq \frac1n\]
Since the series $\sum \frac1{n}$ diverges by the $p$-test, the series $\sum \frac{2n}{n^2+1}$ diverges by the Direct Comparison Test.

\subsection*{Solution 3}

The series $\sum \frac1{n}$ diverges by the $p$-test. Let $a_n = \frac{2n}{n^2+1}$ and $b_n = \frac1{n}$.
\begin{align*}
\lim_{n \to \infty} \frac{a_n}{b_n}
&= \lim_{n \to \infty} \frac{2n^2}{n^2+1}\\
&= \lim_{n \to \infty} \frac{4n}{4n} \text{ by l'hopital}\\
&= \lim_{n \to \infty} \frac44 \text{ by algebra}\\
&= 1
\end{align*}
The Limit Comparison Test applies, since this limit was a positive, finite number. Therefore, the series $\sum \frac{2n}{n^2+1}$ diverges by the Limit Comparison Test.




\end{document}%%%%%%%%%%%%%%%%%

\begin{align*}
L&=\lim_{n \to \infty} \sqrt[n]{|a_n|}\\
&= \lim_{n \to \infty} \sqrt[n]{\left| \right|}\\
\end{align*}

\begin{align*}
L&=\lim_{n \to \infty} \left|\frac{a_{n+1}}{a_n}\right|\\
&= \lim_{n \to \infty} \left| \right|\\
\end{align*}

\begin{align*}
\lim_{n \to \infty} a_n
&= \lim_{n \to \infty} \\
\end{align*}


Since $\sum |a_n| = \sum a_n$, the series $\displaystyle \sum_{n=1}^\infty AAAAAAAAAAAAAA$ converges absolutely.

Since $|r| < 1$, the series ...  converges by the Geometric Series Test.

Since $|r| \geq 1$, the series ...  diverges by the Geometric Series Test.

The function $f(x)=\frac{}{}$ is continuous, positive, and decreasing on $[1,\infty)$.

\subsection*{Solution}

