\documentclass{article}
\usepackage{amsmath}
\usepackage[margin=1.0in]{geometry}
\usepackage{xcolor}

\begin{document}

\noindent
Does $\displaystyle \sum_{n=1}^\infty \frac{(-1)^nn}{n+1}$
diverge, converge absolutely, or converge conditionally?

\subsection*{Note}

While the series $\displaystyle \sum_{n=1}^\infty \frac{(-1)^nn}{n+1}$ is alternating, the sequence $b_n = |a_n| = \frac{n}{n+1}$ satisfies NEITHER property: $b_n$ is not decreasing and the sequence $b_n$ does not have limit zero. So the Alternating Series Test doesn't apply. {\color{red} It is not at this point that we declare the series to diverge. Rather, trying the Alternating Series Test made sense because we had an alternating series, but the problem is that we got NO INFORMATION.} We must try a different test.

\subsection*{Solution}

\begin{align*}
\lim_{n \to \infty} a_n
&= \lim_{n \to \infty} \frac{(-1)^nn}{n+1}
\end{align*}
does not exist (as we get every other term of this sequence to be a number close to $1$ and every other term of this sequence to be a number close to $-1$). Since $\displaystyle \lim_{n \to \infty} a_n$ does not exist, the series $\displaystyle \sum_{n=1}^\infty \frac{(-1)^nn}{n+1}$ diverges by the Test for Divergence.



\end{document}%%%%%%%%%%%%%%%%%

\begin{align*}
L&=\lim_{n \to \infty} \sqrt[n]{|a_n|}\\
&= \lim_{n \to \infty} \sqrt[n]{\left| \right|}\\
\end{align*}

\begin{align*}
\lim_{n \to \infty} a_n
&= \lim_{n \to \infty} \\
\end{align*}


Since $\sum |a_n| = \sum a_n$, the series $\displaystyle \sum_{n=1}^\infty AAAAAAAAAAAAAA$ converges absolutely.

Since $|r| < 1$, the series ...  converges by the Geometric Series Test.

Since $|r| \geq 1$, the series ...  diverges by the Geometric Series Test.

The function $f(x)=\frac{}{}$ is continuous, positive, and decreasing on $[1,\infty)$.

\subsection*{Solution}

